---
title: "SingleCellDesk Example Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(Seurat)
library(ggplot2)
library(patchwork)
```

## 📥 Choose Dataset Format

Set the variable below to either `"10x"` or `"GSE165722"` depending on your dataset:

```{r choose-loader}
# Set dataset type: "10x" for Cell Ranger-style, "GSE165722" for customized format
#dataset_type <- "10x"
dataset_type <- "GSE165722"

if (dataset_type == "10x") {
  source("scripts/00_load_all_samples.R")
} else if (dataset_type == "GSE165722") {
  source("scripts/GSE165722/00_load_all_samples.R")
} else {
  stop("Invalid dataset_type selected")
}
```

## 🔬 Step 1: Quality Control

```{r step1-qc}
source("scripts/GSE165722/01_qc_filtering.R")
```

## 🔬 Step 2: Normalization and Clustering

```{r step2-cluster}
source("scripts/02_normalization_clustering.R")
```

## 🔬 Step 3: Marker Identification and Annotation

```{r step3-annotation}
source("scripts/03_annotation_markers.R")
```

## 🔬 Step 4: Pseudotime Inference with Monocle3

```{r step4-pseudotime}
source("scripts/04_trajectory_monocle.R")
```

## 🔬 Step 5: Cell-Cell Communication with CellChat

```{r step5-cellchat}
source("scripts/05_cellchat_interaction.R")
```

## 📊 Step 6: Summary Plots

```{r step6-plots}
source("scripts/06_plots_summary.R")
```

## 📌 Notes

- For GSE165722, the `.counts.tsv.gz` and `.cellname.txt.gz` pairs are expected in `data/GSE165722/extracted/`
- For 10x, use individual `filtered_feature_bc_matrix/` directories for each sample.